Multiple sequence alignment

### 2023-05-22 episodes/introduction.Rmd
Adding a MSA episode and a suitable file

Answer the quiz as you follow along, using this [link][https://pollev.com/lionelguy323/]
or by using the following QR code 
![QR code](fig/qr_code_quiz.png){alt='QR code linking to the interactive quiz'}

>>>>

Answer the quiz as you follow along, using this [link](https://pollev.com/lionelguy323/)
or by using the following QR code 
![QR code](fig/qr_code_quiz.png){alt='QR code linking to the interactive quiz'}

### 2023-05-22 episodes/msa.Rmd
Adding a MSA episode and a suitable file

---
title: 'episode_example'
teaching: 10
exercises: 2
---

@@

- How do you write a lesson using R Markdown and `{sandpaper}`?

@@

- Explain how to use markdown with the new lesson template
- Demonstrate how to include pieces of code, figures, and nested challenge blocks

@@

This is a lesson created via The Carpentries Workbench. It is written in
[Pandoc-flavored Markdown][pandoc] for static files (with extension `.md`) and
[R Markdown][r-markdown] for dynamic files that can render code into output
(with extension `.Rmd`). Please refer to the [Introduction to The Carpentries
Workbench][carpentries-workbench] for full documentation.

What you need to know is that there are three sections required for a valid
Carpentries lesson template:

 1. `questions` are displayed at the beginning of the episode to prime the
    learner for the content.
 2. `objectives` are the learning objectives for an episode displayed with
    the questions.
 3. `keypoints` are displayed at the end of the episode to reinforce the
    objectives.

:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::: instructor

Inline instructor notes can help inform instructors of timing challenges
associated with the lessons. They appear in the "Instructor View"

::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

>>>>

---
title: 'Multiple sequence alignment'
teaching: 10
exercises: 30
---

@@

- How do you align multiple sequences?
- Why is it important to properly align sequences?

@@

- Use `mafft` to align multiple sequences.
- Test different algorithms.

@@
